% !TEX root = main.tex
\documentclass[sigconf,review]{acmart}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%\setcopyright{acmcopyright}
%\copyrightyear{2023}
%\acmYear{2023}
%\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[ICSE 2024]{46th International Conference on Software Engineering}{April 2024}{Lisbon, Portugal}
%%
%%  Uncomment \acmBooktitle if the title of the proceedings is different
%%  from ``Proceedings of ...''!
%%
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%% June 03--05, 2018, Woodstock, NY}
%\acmPrice{15.00}
%\acmISBN{978-1-4503-XXXX-X/18/06}

\input{preamble.tex}

\begin{document}

\title{Appendix of ``Energy Patterns for Web: An Exploratory Study''}

\author{Pooja Rani}
\email{rani@ifi.uzh.ch}
\affiliation{%
  \institution{University of Zurich}
  \city{Zurich}
  \country{Switzerland}
}

\author{Jonas Zellweger}
\email{jonas.zellweger@uzh.ch}
\affiliation{%
  \institution{University of Zurich}
  \city{Zurich}
  \country{Switzerland}
}

\author{Veronika Kousadianos}
\email{veronika.wu@students.unibe.ch}
\affiliation{%
 \institution{University of Bern}
 \city{Bern}
\country{Switzerland}
 }
 
 
 \author{Luis Cruz}
 %\email{L.Cruz@tudelft.nl}
\affiliation{%
 \institution{Delft University of Technology }
  \city{Delft}
\country{The Netherlands}
}

\author{Timo Kehrer}
\affiliation{%
 \institution{University of Bern}
 \city{Bern, Switzerland}
\country{Switzerland}
 }
 
\author{Alberto Bacchelli}
\affiliation{%
  \institution{University of Zurich, Switzerland}
  \city{Zurich}
  \country{Switzerland}
}

\begin{abstract}
As the energy footprint generated by software is increasing at an alarming rate, understanding how to develop energy-efficient applications has become necessary.
To develop energy-efficient code, previous work has introduced catalogs of coding practices, also known as energy patterns.
These patterns are yet limited to Mobile or third-party libraries.
In this study, we focus on the Web domain---a main source of energy consumption.
First we investigated whether and how Mobile energy patterns can be ported to this domain and found that 20 patterns could be ported.
Then, we interviewed six expert web developers from different companies to challenge the ported patterns.
To quantify the effect of Web energy patterns on energy consumption, we set up an automated pipeline to evaluate two ported patterns: `Dynamic Retry Delay' (DRD) and  Open Only When Necessary (OOWN). 
In this document, we describe the steps to obtain the artifact package of our study, the artifact material, and how to use the artifact.
\end{abstract}

\maketitle

\input{appendix.tex}
\bibliographystyle{ACM-Reference-Format}
\bibliography{references}
\end{document}


